Pre-Project Review

### 2021-11-19 article/article.tex
Change bibliography style

\documentclass[sotoncolour]{uosarticle}
\graphicspath{{../figures/}}
\usepackage[round]{natbib}
\hypersetup{colorlinks=true}
%% ----------------------------------------------------------------
%% --------------------THESIS/DOC INFORMATION ---------------------
%\faculty     {Faculty of Science}
%\FACULTY     {\MakeUppercase{\facname}}
\department  {School of Physics and Astronomy}
\DEPARTMENT  {\MakeUppercase{\deptname}}
%\group       {[Group name]}
%\GROUP       {\MakeUppercase{\groupname}}
\title       {BSc Pre-Project Review}
\modulename  {PH4111}
\authors     {180014855}
\date        {\today}

\begin{document}
%% ------------------ FRONT MATTER ORGANISATION -------------------
\frontmatter
\maketitle
\begin{abstract}
This work is about \dots
\end{abstract}
\mainmatter
%% ------------------ MAIN MATTER (CONTENT) --------------------
\section{Introduction} \label{sec:Introduction}
Insert introduction here.

\section{Conclusions} \label{sec:Conclusions}
Draw conclusions here.
\acknowledgements{Thanks to ...}
\backmatter
\appendix
\bibliographystyle{plainnat}
\bibliography{UOS}
%% ----------------------------------------------------------------
\section{Stuff} \label{Section:Stuff}
Insert stuff here.
\end{document}
%% ----------------------------------------------------------------

>>>>

\documentclass[sotoncolour]{uosarticle}
\graphicspath{{../figures/}}
\hypersetup{colorlinks=true}

\usepackage[
    backend=biber,
    style=phys,
    natbib=true,
    url=false, 
    doi=false,
    eprint=false,
    autocite=superscript
]{biblatex}
\addbibresource{references.bib}

\department  {School of Physics and Astronomy}
\title       {Pre-Project Review}
\modulename  {PH4111}
\authors     {180014855}
\date        {\today}

\begin{document}
\frontmatter
\maketitle
\begin{abstract}
This work is about \dots
\end{abstract}

\mainmatter

\section{Introduction} \label{sec:Introduction}
Why millimetre waves?
Mention the meteorological radar range equation.
Brief mention of Rayleigh scattering.
The meteorological radar range equation, derived by Probert-Jones in 1962, is\supercite{ProbertJones}
\begin{equation}
	y = m x + c\label{eqn:MeteoRange}
\end{equation}

\section{Pulse Doppler radar} \label{sec:PulseDopperRadar}

\section{Continuous wave radar} \label{sec:CWR}

\section{Frequency-modulated continuous wave radar} \label{sec:FMCWR}

\section{Conclusions} \label{sec:Conclusions}

\backmatter
\printbibliography
\end{document}
